Evolutionary Computing and Machine Learning

### 2018-08-29 AI/EC.tex
8.29

\title{Evolutionary Computing and Machine Learning}
\author{陈辉}
\date{}
\begin{document}
\maketitle
\tableofcontents
\newpage
\part{文献}
\section{\textit{Simple-Evolutionary-Optimization-Can-Rival-Stochastic-Gradient-Descent-in-Neural-Networks}}
\paper{Simple-Evolutionary-Optimization-Can-Rival-Stochastic-Gradient-Descent-in-Neural-Networks}{1}

\includepdf[link=true,pages=-,fitpaper]{./papers/Simple-Evolutionary-Optimization-Can-Rival-Stochastic-Gradient-Descent-in-Neural-Networks.pdf}
%\includepdf[link=true,pages=-,fitpaper]{./papers/<++>.pdf}
%\includepdf[link=true,pages=-,fitpaper,angle=-90]{./papers/<++>.pdf}

>>>>

\title{Evolutionary Computing and Machine Learning}
\author{陈辉}
\date{}
\begin{document}
\maketitle
\tableofcontents
\newpage
\part{文献}
\section{\textit{Population-Based-Training-of-Neural-Networks}}
\paper{Population-Based-Training-of-Neural-Networks}{1}
\subsection{Introduction}
\paragraph{Keypoints of The Problem}

\begin{itemize}
		\item Hyperparameters tuning is essential.
		\href{https://en.wikipedia.org/wiki/Hyperparameter\_optimization}{Wiki}.
		\item Non-stationary problems might lead to non-stationary hyperparameters.
		\item Tow main tuning tracks:
\begin{itemize}
		\item Parallel search. 
		\item Sequential search.
\end{itemize}
\end{itemize}

\paragraph{Brief Introduction to PBT}
\paragraph{What PBT can do}

\subsection{Related Work}

\section{\textit{Simple-Evolutionary-Optimization-Can-Rival-Stochastic-Gradient-Descent-in-Neural-Networks}}
\paper{Simple-Evolutionary-Optimization-Can-Rival-Stochastic-Gradient-Descent-in-Neural-Networks}{1}

\includepdf[link=true,pages=-,fitpaper]{./papers/Population-Based-Training-of-Neural-Networks.pdf}
\includepdf[link=true,pages=-,fitpaper]{./papers/Simple-Evolutionary-Optimization-Can-Rival-Stochastic-Gradient-Descent-in-Neural-Networks.pdf}
%\includepdf[link=true,pages=-,fitpaper]{./papers/<++>.pdf}
%\includepdf[link=true,pages=-,fitpaper,angle=-90]{./papers/<++>.pdf}
